---
title: "Week 7 Activity"
author: "2023 FIRE298: Sustainability Analytics"
format: html
editor: visual
---

### Install required packages

```{r}
install.packages("terra")
install.packages("tidyverse")
install.packages("remotes")
install.packages("readxl")
```

### Declare that you will use the packages

```{r}
library("terra")
library("tidyverse")
library("remotes")
library("readxl")
```

### Upload an excel file into the Environment

Upload an excel file from Google Drive into the Environment.

Note: Skip this method if you are using Posit Cloud.

```{r}

```

Posit Cloud method to upload an excel file into the Environment.

Note: This method will only work if the excel file exists in the GitHub repository.

```{r}
Africa_1997_2023_Sep22<-read_excel("Africa_1997-2023_Sep22.xlsx")
```

### **Upload a shapefile into the Environment**

Upload a shapefile from either:

```         
"G:/Shared drives/2023 FIRE-SA/FALL OUTPUT/Mining/DATA/Democratic_Republic_of_the_Congo_mining_permits/Democratic_Republic_of_the_Congo_mining_permits.shp"
```

or

```         
"Democratic_Republic_of_the_Congo_mining_permits/Democratic_Republic_of_the_Congo_mining_permits.shp"
```

into the Environment.

```{r}
p<-vect("Democratic_Republic_of_the_Congo_mining_permits/Democratic_Republic_of_the_Congo_mining_permits.shp")
```

### Map conflicts in the DRC

```{r}
acl<-Africa_1997_2023_Sep22 %>%
  filter(COUNTRY=="Democratic Republic of Congo")

names(acl)

acl_points<-vect(acl, 
               geom=c("LONGITUDE", "LATITUDE"), 
               crs="+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ")

plot(acl_points)
```

### Plot permit locations and conflicts together

```{r}
plot(acl_points, "EVENT_TYPE", 
     col=rainbow(6), 
     cex=0.1)
plot(p, add=TRUE)
```

### Create 10 km buffer around the centroid of each permit

```{r}
pc<-centroids(p)

crs(p)

pcb<-buffer(pc, width=10000, capstyle="round")
```

### Understand shapefile dimensions

```{r}
dim(pcb)

dim(acl_points)
```

### Find conflict events within permit row 7170

```{r}
i<-terra::relate(pcb[7170], acl_points, relation="intersects")
```

### **Inspect intersection output**

```{r}
dim(i)
sum(i) #there are 40 true values
```

### Identify conflicts within permit row 7170

```{r}
vi<-as.vector(i)
acl_in_p7170<-acl[vi,]
```
